pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single cell RNA-seq preprocessing tools

### 2020-08-06 bmc_article.tex
Updates from Overleaf

While most methods accurately identified the doublets in the 3 cell lines dataset (mixology10x3cl), the other two datasets proved more difficult (Figure \ref{fig:doublets}A). \textit{scDblFinder} achieved comparable or better accuracy than top alternatives while being the fastest method (Figure \ref{fig:doublets}B). Across datasets, cells called as doublets tended to be classified in the wrong cluster more often than other cells (Figure \ref{fig:doublets}C). We also found that {\color{red} \textit{scDblFinder} clearly improved the accuracy of the clustering across datasets that are expected to have heterotypic doublets (mixology datasets), and even in a simulation (simMix1) that should not contain any (Figure \ref{fig:filtering}). Across the datasets that, being FACS-sorted, should not contain such doublets, doublet removal tended not to robustly impact clustering accuracy, however in few datasets (ZhengMix4eq and Zhengmix4uneq, and simMix2 with a very small difference) doublet removal performed worse when combined with lenient or no filtering.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.55\textwidth, keepaspectratio]{{anova.pdf}}
    \caption{{\color{red}\textbf{Variance in clustering metrics explained by the parameters.} Proportion of variance explained by the parameters of the main analysis steps. The proportions are calculated from an ANOVA using the model;\\
    \texttt{metric$\sim$ dataset*resolution+doubletmethod+filt+norm+clustmethod+dims}
    \\ and substracting the variance attributable to differences due to datasets, resolutions and their interactions. }}
    \label{fig:overall}
\end{figure}

>>>>

While most methods accurately identified the doublets in the 3 cell lines dataset (mixology10x3cl), the other two datasets proved more difficult (Figure \ref{fig:doublets}A). \textit{scDblFinder} achieved comparable or better accuracy than top alternatives while being the fastest method (Figure \ref{fig:doublets}B). Across datasets, cells called as doublets tended to be classified in the wrong cluster more often than other cells (Figure \ref{fig:doublets}C). We also found that {\color{red} \textit{scDblFinder} clearly improved the accuracy of the clustering across datasets that are expected to have heterotypic doublets (mixology datasets), and even in a simulation (simMix1) that should not contain any (Figure \ref{fig:filtering}). Across the datasets that, being FACS-sorted, should not contain such doublets, doublet removal tended not to robustly impact clustering accuracy. However in few datasets (ZhengMix4eq and Zhengmix4uneq, and simMix2 with a very small difference) doublet removal performed worse when combined with lenient or no filtering.}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.55\textwidth, keepaspectratio]{{anova.pdf}}
    \caption{\color{red}\textbf{Variance in clustering metrics explained by the parameters.} Proportion of variance explained by the parameters of the main analysis steps. The proportions are calculated from an ANOVA using the model;
    \texttt{metric $\sim$ dataset*resolution+doubletmethod+filt+norm+clustmethod+dims}
    and substracting the variance attributable to differences due to datasets, resolutions and their interactions. }
    \label{fig:overall}
\end{figure}
